---
output:
  pdf_document: default
  html_document: default
---
```{r message=FALSE, warning=FALSE}
options(warn = -1)
library(tidyverse)
library(ggthemes)
library(ggplot2)
library(tidymodels)
library(corrplot)
library(yardstick)
library(ISLR)
library(ISLR2)
library(discrim)
library(corrr)
tidymodels_prefer()
```

```{r}
titanic <- read.csv(file="/Users/honchowayne/Desktop/titanic.csv")
titanic %>% head()
```

```{r}
titanic$survived <- as.factor(titanic$survived)
titanic$survived <- factor(titanic$survived, levels = c("Yes" , "No"))
titanic$pclass <- as.factor(titanic$pclass)
titanic$sex <- as.factor(titanic$sex)
```

Question1: Split the data
```{r}
set.seed(3435)
titanic_split <- initial_split(titanic,strata = survived, prop = 0.80)
titanic_train <- training(titanic_split)
titanic_test <- testing(titanic_split)
titanic_split
```
```{r}
dim(titanic_train) #number seems right to me
```
```{r}
dim(titanic_test) #number match the Assess number
```

Question2: Fold the training data, k=10
```{r}
  
titanic_rec <- recipe(survived ~ pclass + sex + age + sib_sp + parch + fare, data = titanic_train) %>% 
  step_impute_linear(age) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_interact(terms =  ~ sex_male:fare) %>% 
  step_interact(terms =  ~ age:fare)
```
```{r}
set.seed(3534)
titanic_folds <- vfold_cv(titanic_train, v=10)
titanic_folds
```

Question3:

1. We could have the chance to use all of our data by applying this method. 
Generally, compared to traditional fitting and testing model on the entire 
training set, we get to  build K different models, so we are able to make 
predictions on all of our data. 

   The second reason I could think of is that we can be more confident in our 
algorithm performance. When we do a single evaluation on our test set, 
we get only one result. This result may be because of chance or a biased test 
set for some reason. By training five (or ten) different models we can 
understand better what’s going on.

2. If we did use the entire training set, the resampling method is validation 
set approach

Question4:
```{r}
#1
log_reg_titanic <- logistic_reg() %>% 
  set_engine("glm") %>% 
  set_mode("classification")

log_wkf<-workflow() %>% 
  add_model(log_reg_titanic) %>% 
  add_recipe(titanic_rec)

#2
lda_mod_titanic <- discrim_linear() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")

lda_wkf<-workflow() %>% 
  add_model(lda_mod_titanic) %>% 
  add_recipe(titanic_rec)

#3
qda_mod_titanic <- discrim_quad() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")

qda_wkf<-workflow() %>% 
  add_model(qda_mod_titanic) %>% 
  add_recipe(titanic_rec)

#The total folds is going to be 30 (3x10)
```

Question5:
```{r}
log_fit_rs <- log_wkf %>% 
  fit_resamples(titanic_folds)

lda_fit_rs <- lda_wkf %>% 
  fit_resamples(titanic_folds)

qda_fit_rs <- qda_wkf %>% 
  fit_resamples(titanic_folds)
```

Question7:
```{r}
log_metrics <- collect_metrics(log_fit_rs)
log_metrics
```
```{r}
lda_metrics <- collect_metrics(lda_fit_rs)
lda_metrics
```
```{r}
qda_metrics <- collect_metrics(qda_fit_rs)
qda_metrics
```
The logistic regression analysis is the best model among 
these three because it has the highest accuracy mean.

Question7: fit the model, using training dataset

```{r}
final_fit <- fit(log_wkf, titanic_train)
final_fit
```
```{r}
predict(final_fit, new_data = titanic_train, type = "prob")
```
```{r}
train_acc <- augment(final_fit, new_data = titanic_train) %>% 
  accuracy(truth = survived, estimate=.pred_class)
train_acc
```

Question8:
```{r}
predict(final_fit, titanic_test, type = "prob")
```
```{r}
test_acc <- augment(final_fit, new_data = titanic_test) %>% 
  accuracy(truth = survived, estimate = .pred_class)
test_acc
```
```{r}
compare <- bind_cols(log_metrics[1,3], test_acc$.estimate) 
names(compare)[1] <- "average folds accuracy"
names(compare)[2] <- "testing accuracy"
compare
```





























